Notes on Control Plane Inference

### 2021-05-18 inference.tex
Create topology

\usepackage[margin=1in]{geometry}
\usepackage{halloweenmath}
\usepackage{amsmath, amssymb, amsthm, array, stmaryrd}
\usepackage{wasysym}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{float}
\usepackage{scalerel}
%% \usepackage[notext,not1,nomath]{stix}
\usepackage{enumitem}

@@

% sets
\newcommand{\Value}{\mathsf{Value}}
\newcommand{\BVExpr}{\mathsf{BVExpr}}
\newcommand{\BExpr}{\mathsf{BExpr}}
\newcommand{\Cmd}{\mathsf{Cmd}}
\newcommand{\Action}{\mathsf{Action}}
\newcommand{\Instr}{\mathsf{Instr}}
\newcommand{\Prog}{\mathsf{Prog}}
\newcommand{\GCL}{\mathsf{GCL}}
\newcommand{\Pkt}{\mathsf{Pkt}}
\newcommand{\Model}{\mathsf{Model}}
\newcommand{\Hdr}{\mathsf{Hdr}}
\newcommand{\Field}{\mathsf{Field}}
\newcommand{\Table}{\mathsf{Table}}
\newcommand{\Row}{\mathsf{Row}}
\newcommand{\List}{\mathsf{List}}
\newcommand{\Var}{\mathsf{Var}}
\newcommand{\SymbRow}{\mathsf{SymbRow}}

@@

% Theorems
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}

@@

\begin{figure}[htp]
  \[\begin{array}{lclll}
    \multicolumn{3}{l}{\Value} \\
    v & ::= & [n]_w  & \textit{Bitvector Literal} & (a,g,p,\iota) \\
    \multicolumn{3}{l}{\SymbRow} \\
    \rho & ::= & \left\{
    \begin{array}{l}
      \matches = \List[x];\\
      \action = x;\\
      \data = \List[x]
    \end{array}\right\} & \textit{Symbolic Row} & (\iota)\\
    \multicolumn{3}{l}{\BVExpr} \\
    e & ::= & v & \textit{Value} & (a,g,p,\iota)\\
      & \mid & h.f & \textit{Header Access} & (a,g,p,\iota)\\
      & \mid & \rho.\matches[i] & \textit{Symbolic Match} & (\iota)\\
      & \mid & \rho.\action & \textit{Symbolic Action} & (\iota) \\
      & \mid & \rho.\data[i] & \textit{Symbolic Action Data} & (\iota) \\
      & \mid & x & \textit{Action Data Variable} & (a^*) \\
      & \mid & e \binop e & \textit{Arbitrary Binary Operation} & (a,g,p,\iota) \\
    & \mid & \unop e & \textit{Arbitrary Unary Operation} & (a,g,p,\iota) \\
    \multicolumn{3}{l}{\Table} \\
    t & ::= & \left\{\begin{array}{l}
    t.\id = v; \\
    t.\keys = \List[h.f]; \\
    t.\actions = \List[\lambda \vec x.\,a]\\
    \end{array}\right\} & \textit{Table} & (p)\\
    \multicolumn{3}{l}{\BExpr} \\
    b & ::= & \FALSE  & \textit{Absurdity}& (a,g,p,\iota)\\
      & \mid & b \Rightarrow b & \textit{Implication} & (a,g,p,\iota)\\
    & \mid & e = e & \textit{Bitvector Equality} & (a,g,p,\iota)\\
    & \mid & \rho \in t & \textit{Table membership} & (\iota)\\
    & \mid & \forall \rho.~b & \textit{Row Universality} & (\iota)\\
    \multicolumn{4}{l}{c \in \Cmd, a \in \Action, g \in \GCL, p \in \Prog, \iota \in \Instr } \\
    c & ::=  & h.f := e & \textit{Assignment} & (g,p,\iota) \\
      %% & \mid & \havoc \rho & \textit{Row Havoc} & (\iota) \\
      & \mid & \assert b & \textit{Assertion} & (g,p,\iota)\\
      & \mid & \assume b & \textit{Assumption} & (g,p,\iota) \\
      & \mid & t.\apply() & \textit{Table Application} & (p)\\
      & \mid & c;c & \textit{Sequential Composition} & (a,g,p,\iota) \\
      & \mid & c \choice c & \textit{Nondeterministic Choice} & (g,p,\iota)\\
      %% & \mid & \{c\} & \textit{Scope} & (g,p,\iota)\\
    \multicolumn{3}{l}{
      \begin{array}{ll}
        x \in \Var & h \in \Hdr\\
        n,w,i \in \mathbb{N} & f \in \Field
    \end{array}} & \textit{Sets }\\
  \end{array}
\]
\caption{Grammar of Commands $c \in \Cmd$. Legal action indicated by $a \in
  \Action$, legal instrumented command variants indicated by $\iota \in \Instr$,
  dataplane programs indicated by $p \in \Prog$, and table-free commands
  indicated by $g \in \GCL$.}
\label{fig:grammar}
\end{figure}

@@

\begin{figure}
  \[\begin{array}{l>{\iff}cl}
  \satisfy \sigma \pkt \mu \FALSE && \textit{pigs fly} \\
  \satisfy \sigma \pkt \mu b_1 \Rightarrow b_2 &&
  \notsatisfy \sigma \pkt \mu  b_1~\textit{or}~
  \satisfy \sigma \pkt \mu b_2\\
  \satisfy \sigma \pkt \mu e_1 = e_2 &&
  \edenote{e_1}~\pkt~\mu = \edenote{e_2}~\pkt~\mu, \qquad
  \text{(note strict semantics)} \\
  \satisfy\sigma\pkt\mu \rho \in t. && \mu(\rho) \in \sigma(t.\id) \\
  \satisfy \sigma \pkt \mu \forall \rho. ~b &&
  \forall r.
  \satisfy \sigma \pkt {\mu\{\rho \mapsto r\}} b
  \end{array}
  \]
  \todo[inline]{Clarify $\error$ states}
  \caption{Satisfaction for $\BExpr$.}
  \label{fig:bool-satis}
\end{figure}

@@

\begin{figure}[htp]
  \[\begin{array}{l >{\triangleq}cl}
  \multicolumn{3}{l}{\denote{c}^\sigma : \Model \to \Pkt \to \mathcal{P}(\Model \times \Pkt)_\error }\\
    \denote{h.f := e}^\sigma\,\mu\,\pkt && \{(\mu, \pkt\{h \mapsto v\} \mid v \in \edenote{e}\,\mu\,\pkt\})\} \\
    \denote{\assume b}^\sigma\,\mu\,\pkt &&
    \begin{cases}
      \{(\mu,\pkt)\} & \satisfy \sigma \pkt \mu b \\
      \{\} & \textit{otherwise} \\
    \end{cases}\\
    \denote{\assert b}^\sigma\,\mu\,\pkt &&
    \begin{cases}
      \{(\mu,\pkt)\} & \satisfy \sigma \pkt \mu b \\
      \error & \textit{otherwise}
    \end{cases} \\
    %% \denote{\havoc \rho}^\sigma\,\mu\,\pkt &&
    %% \{(\mu\{\rho \mapsto r\}, \pkt) \mid r \in \Row\} \\
    \denote{c_1;c_2}^\sigma\,\mu\,\pkt&&
    \bigcup_{(\mu',\pkt') \in \denote{c_1}^\sigma\,\mu\,\pkt}\denote{c_2}^\sigma\,\mu'\,\pkt' \\
    \denote{c_1 \choice c_2}^\sigma\,\mu\,\pkt &&
    \denote{c_1}^\sigma\,\mu\,\pkt \cup \denote{c_2}^\sigma\,\mu\,\pkt \\
    %% \denote{\{c\}}^\sigma\,\mu\,\pkt &&
    %% \{(\mu,\pkt') \mid (\mu',\pkt') \in \denote{c}^\sigma\,\mu\,\pkt \}\\
    \denote{t.\apply()}^\sigma\,\mu\,\pkt &&
    \begin{cases}
      \denote{c[\vec d/\vec x]}^\sigma\,\mu\,\pkt,
      & \text{where}~\lambda \vec x.~c = r.\action, \vec d = r.\data \\
      & \text{where}~r = \argmin_i\{\satisfy \sigma \pkt \mu b_i\} \\
      & \text{where}~b_i = \sigma(t.\id)[i].\matches = t.\keys \\
      \{(\mu,\pkt)\}, & \mathit{otherwise}
    \end{cases}
  \end{array}\]
  \caption{Semantics of Commands}
  \label{fig:com-sem}
\end{figure}

@@

This means that we must check the validity of \[\state\sigma_c \Rightarrow
\WP(c\instr,\TRUE)\]

@@

Now we can formally define the research problems that we want to solve. We have
some ideal goals, that are probably not solvable in general.

\begin{quote}
  \textbf{Conservative Problem.} Given a command $c \in \Cmd$, compute the weakest test
  $b$ such that if, for a state $\sigma : \Value \to \Row^*$, the following
  judgement is valid \[\state\sigma_c \Rightarrow b,\] then \[\forall \pkt \in \Pkt.~
  \denote{c}^\sigma \emptyset\,\pkt \neq \error \]
\end{quote}

However, this $b$ may be $\FALSE$ for many realistic programs $c$, so we may
prefer to solve the following problem:

\begin{quote}
  \textbf{Flexible Problem.} Given a command $c \in \Cmd$, compute a test
  $b_{\mathit{cp}}$, and a test $b_{\mathit{pkt}}$ such that for every packet
  $\pkt \in \Pkt$ and state $\sigma : \Value \to \Row^*$, if the following
  formula is valid
  \[b_{\mathit{pkt}} \wedge \state\sigma_c \Rightarrow b_{\mathit{cp}},\]
  then \[\denote{c}^\sigma\emptyset\,\pkt \neq \error \]
\end{quote}

\section{Reduction to QE}

We can observe that the \textbf{Conservative Problem} is simply solvable by
reduction to Quantifier Elimination. In fact Quantifier elimination is one of
the key driving forces of the Dillig/Dillig/Millstein abduction work (\textsc{Hola},
\textsc{Explain}). We sketch the argument here.

@@

This \emph{probably} doesn't work in general. Standard QE procedures are
exponential at best, and enumerating all eth/ipv4 src/dst addresses already
takes an intractable amount of time.

The Dilligs' line of work uses Presburger arithmetic QE to implement the
quantifier elimination scheme. We could directly adopt this, however networking
programs make heavy use of bitwise operators like XOR, so we need to take a
different strategy.
StackOverflow\footnote{https://stackoverflow.com/questions/21293278/mathematical-arithmetic-representation-of-xor}
says that you can implement $a \mathbin{\texttt{XOR}} b$ as $a + b - ab(1 + a +
b - ab)$, but that still takes us out of PA, and casting between the naturals
and fixed-width bitvectors seems dangerous.

\section{Can Templates save us?}

One option is to use a kind of constrained template-based synthesis, where we
generate a catalogue of temaplates based on syntactic features of the target table.

@@

To do so, we need to extend our templates along the following dimensions:
\begin{enumerate}[align=left]
\item[\textbf{Keys}.] Should generalize by changing the LHS comparisons to $
  \bigwedge_i[\rho.\keys[i]~\square_{\{=,\neq\}}~?_{v_i}]?$
\item[\textbf{Action Data}.] Should generalize by changing the RHS comparisons to $\bigwedge_i[\rho.\data[i]~\square_{\{=,\neq\}}~?_{v_i}]?$
\item[\textbf{Actions}.] We need to generalize the template across multiple actions. This should be as simple as adding $\rho.\action = i$ on the RHS of each implication above.
\item[\textbf{Sequence}.] I'm not sure how to generalize sequentially composed tables.
  Perhaps a larger catalogue of templates conditioned on structural information:
  if we notice that $t_1$ has a dataflow path to the keys of $t_2$, we should
  generate a join condition template, otherwise we may be able to simply ``and'' the templates.

\item[\textbf{Nondeterminism} ($c_1 \choice c_2$).] To solve the \textbf{Conservative
  Problem} we simply and the templates together, but to solve the
  \textbf{Flexible Problem} we may be able to constrain the problem (by
  constraining the packets) to either $c_1$ or $c_2$. This would require
  computing a $b_{\textit{pkt}}$.
\end{enumerate}

\end{document}

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm, array, stmaryrd}
\usepackage{wasysym}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{float}
\usepackage{scalerel}
%% \usepackage[notext,not1,nomath]{stix}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{soul}

@@

% sets
\newcommand{\Value}{\mathsf{Value}}
\newcommand{\BVExpr}{\mathsf{BVExpr}}
\newcommand{\BExpr}{\mathsf{BExpr}}
\newcommand{\Cmd}{\mathsf{Cmd}}
\newcommand{\Action}{\mathsf{Action}}
\newcommand{\Instr}{\mathsf{Instr}}
\newcommand{\Prog}{\mathsf{Prog}}
\newcommand{\GCL}{\mathsf{GCL}}
\newcommand{\Pkt}{\mathsf{Pkt}}
\newcommand{\Model}{\mathsf{Model}}
\newcommand{\Hdr}{\mathsf{Hdr}}
\newcommand{\Field}{\mathsf{Field}}
\newcommand{\Table}{\mathsf{Table}}
\newcommand{\Row}{\mathsf{Row}}
\newcommand{\List}{\mathsf{List}}
\newcommand{\Var}{\mathsf{Var}}
\newcommand{\SymbRow}{\mathsf{SymbRow}}
\newcommand{\State}{\mathsf{State}}

@@

% Theorems
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}{Definition}

@@

\begin{figure}[htp]
  \[\begin{array}{lclll}
    \multicolumn{3}{l}{\Value} \\
    v & ::= & [n]_w  & \textit{Bitvector Literal} \\
    \multicolumn{3}{l}{\SymbRow} \\
    \rho & ::= & \left\{
    \begin{array}{l}
      \matches = \List[x];\\
      \action = x;\\
      \data = \List[x]
    \end{array}\right\} & \textit{Symbolic Row} \\
    \multicolumn{3}{l}{\BVExpr} \\
    e & ::= & v & \textit{Value} \\
      & \mid & h.f & \textit{Header Access}\\
      & \mid & \rho.\matches[i] & \textit{Symbolic Match}\\
      & \mid & \rho.\action & \textit{Symbolic Action}\\
      & \mid & \rho.\data[i] & \textit{Symbolic Action Data}\\
      & \mid & x & \textit{Action Data Variable}\\
      & \mid & e \binop e & \textit{Arbitrary Binary Operation}\\
    & \mid & \unop e & \textit{Arbitrary Unary Operation} \\
    \multicolumn{3}{l}{\Table} \\
    t & ::= & \left\{\begin{array}{l}
    t.\id = v; \\
    t.\keys = \List[h.f]; \\
    t.\actions = \List[\lambda \vec x.\,a]\\
    \end{array}\right\} & \textit{Table}\\
    \multicolumn{3}{l}{\BExpr} \\
    b & ::= & \FALSE  & \textit{Absurdity}\\
      & \mid & b \Rightarrow b & \textit{Implication}\\
    & \mid & e = e & \textit{Bitvector Equality}\\
    & \mid & \rho \in t & \textit{Table membership}\\
    %% & \mid & \forall \rho.~b & \textit{Row Universality}\\
    \multicolumn{4}{l}{c \in \Cmd, a \in \Action, g \in \GCL, p \in \Prog, \iota \in \Instr } \\
    c & ::=  & h.f := e & \textit{Assignment}\\
      %% & \mid & \havoc \rho & \textit{Row Havoc} & (\iota) \\
      & \mid & \assert b & \textit{Assertion}\\
      & \mid & \assume b & \textit{Assumption} \\
      & \mid & t.\apply() & \textit{Table Application} \\
      & \mid & c;c & \textit{Sequential Composition} \\
      & \mid & c \choice c & \textit{Nondeterministic Choice} \\
      %% & \mid & \{c\} & \textit{Scope} & (g,p,\iota)\\
    \multicolumn{3}{l}{
      \begin{array}{ll}
        x \in \Var & h \in \Hdr\\
        n,w,i \in \mathbb{N} & f \in \Field
    \end{array}} & \textit{Sets }\\
  \end{array}
\]
\caption{Grammar of Commands $c \in \Cmd$.}
\label{fig:grammar}
\end{figure}

@@

@@

\begin{figure}[htp]
  \[\begin{array}{l >{\triangleq}cl}
  \multicolumn{3}{l}{\denote{c}^\sigma : \Pkt \to \mathcal{P}(\Pkt)_\error }\\
    \denote{h.f := e}^\sigma\,\mu\,\pkt && \{(\mu, \pkt\{h \mapsto v\} \mid v \in \edenote{e}\,\mu\,\pkt\})\} \\
    \denote{\assume b}^\sigma\,\mu\,\pkt &&
    \begin{cases}
      \{(\mu,\pkt)\} & \satisfy \sigma \pkt \mu b \\
      \{\} & \textit{otherwise} \\
    \end{cases}\\
    \denote{\assert b}^\sigma\,\mu\,\pkt &&
    \begin{cases}
      \{(\mu,\pkt)\} & \satisfy \sigma \pkt \mu b \\
      \error & \textit{otherwise}
    \end{cases} \\
    %% \denote{\havoc \rho}^\sigma\,\mu\,\pkt &&
    %% \{(\mu\{\rho \mapsto r\}, \pkt) \mid r \in \Row\} \\
    \denote{c_1;c_2}^\sigma\,\mu\,\pkt&&
    \bigcup_{(\mu',\pkt') \in \denote{c_1}^\sigma\,\mu\,\pkt}\denote{c_2}^\sigma\,\mu'\,\pkt' \\
    \denote{c_1 \choice c_2}^\sigma\,\mu\,\pkt &&
    \denote{c_1}^\sigma\,\mu\,\pkt \cup \denote{c_2}^\sigma\,\mu\,\pkt \\
    %% \denote{\{c\}}^\sigma\,\mu\,\pkt &&
    %% \{(\mu,\pkt') \mid (\mu',\pkt') \in \denote{c}^\sigma\,\mu\,\pkt \}\\
    \denote{t.\apply()}^\sigma\,\mu\,\pkt &&
    \begin{cases}
      \denote{c[\vec d/\vec x]}^\sigma\,\mu\,\pkt,
      & \text{where}~\lambda \vec x.~c = r.\action, \vec d = r.\data \\
      & \text{where}~r = \argmin_i\{\satisfy \sigma \pkt \mu b_i\} \\
      & \text{where}~b_i = \sigma(t.\id)[i].\matches = t.\keys \\
      \{(\mu,\pkt)\}, & \mathit{otherwise}
    \end{cases}
  \end{array}\]
  \caption{Semantics of Commands}
  \label{fig:com-sem}
\end{figure}

@@

\begin{conjecture}
  For every $c \in \Cmd$, and $\sigma \in \State$, the following formula is valid
  \[\state\sigma_c \Rightarrow  \WP(c\instr,\TRUE) \iff \WP(c[\sigma], \TRUE)\]
\end{conjecture}

@@

Now we can formally define the research problems that we want to solve. We have
an ideal, that is probably not solvable in general. First we begin by defining a control plane formula.

\begin{definition}[Control Plane Formulae ]
  A control plane formula $\varphi$ is a boolean expression in $\BExpr$ that
  contains no header accesses $h.f$.
\end{definition}

\begin{quote}
  \textbf{Conservative Problem.} Given a command $c \in \Cmd$, compute (the
  weakest) control plane formula $\varphi$ such that if, for a state $\sigma :
  \Value \to \Row^*$, the following judgement is valid \[\state\sigma_c
  \Rightarrow \varphi,\] then \[\forall \pkt \in \Pkt.~ \denote{c}^\sigma
  \emptyset\,\pkt \neq \error \]
\end{quote}

However, this $\phi$ may be $\FALSE$ for many realistic programs $c$, so we may
prefer to solve the following problem:

\begin{quote}
  \textbf{Flexible Problem.} Given a command $c \in \Cmd$, compute (the weakest)
  control plane formula $\varphi$, and a test $b$ such that for every
  packet $\pkt \in \Pkt$ and state $\sigma : \Value \to \Row^*$, if the
  following formula is valid
  \[b \wedge \state\sigma_c \Rightarrow \varphi,\]
  then \[\denote{c}^\sigma\emptyset\,\pkt \neq \error \]
\end{quote}

\section{Quantifier Elimination?}

We can observe that the \textbf{Conservative Problem} is simply solvable by
reduction to Quantifier Elimination. In fact. Quantifier elimination is one of
the key driving forces of the Dilligs' abduction work (\textsc{Hola},
\textsc{Explain}). We sketch the argument here.

@@

\paragraph{Discussion} This \emph{probably} doesn't work in general. Standard QE procedures are
exponential at best, and enumerating all eth/ipv4 src/dst addresses already
takes an intractable amount of time. It's also not clear (to me) that this
solution is weakest.

The Dilligs' line of work uses Presburger arithmetic QE to implement the
quantifier elimination scheme. We could directly adopt this, however networking
programs make heavy use of bitwise operators like XOR, so we need to take a
different strategy.

\section{Data-Driven Precondition Inference?}

It seems that a solution to our problem can also be found in work by
Padhi/Sharma/Millstein entitled \textit{Data-Driven Precondition Inference with
  Learned Features}\todo{This won't make a ton of sense unless you've
  read this paper}. Their algorithm uses a subroutine,
$\textsc{VPreGen}(c,Q,G)$, which takes code $c$, a boolean predicate $Q$,
and a set of passing test inputs $G$ and produces a predicate $P$ such that
$P(t) = \TRUE$ for all $t \in G$, and $\{P\}\,C\,\{Q\}$.

This gets us most of the way there. Naively, let's consider the space of inputs
to be $\State \times \Pkt$. Then let $b_P$ be a boolean expression such that
$b_p = \textsc{VPreGen}(c\instr,\TRUE,\emptyset)$. Then we know $b_P \Rightarrow
\WP(c\instr,\TRUE)$. However, $b_p$ is not \emph{a priori} a control-plane
formula.

There's a trivial fix: modify the feature learning algorithm to only generate
features that are control-plane formulae. The procedure $\textsc{FeatureLearn}$
generates features from a space of operations described by the procedure
$\textsc{GetOperations}()$. If we simply restrict \textsc{GetOperations} so that
it only returns features that are control-plane formulae, then the generated
expression $b_p$ is guaranteed to be a control plane formula. It may also be
prudent to restrict the input space $G$ to be a subset of $\State$, rather than
of $\State \times \Pkt$, but it doesn't seem strictly necessary.

\paragraph{Discussion} This doesn't quite achieve our goal, because the
synthesized solution is not necessarily the weakest. Further, its not clear to
what extent this procedure relies on a non-empty set of examples $G$. Nor is it
immediately clear where we would get such inputs. Currently each iteration of
the \textsc{VPreGen} algorithm augments the set of examples with a failing
example -- if it turns out that good inputs are necessary, it could be augmented
with a similar solver call to generate a positive example (e.g.
$\textsc{Sat}(\WP(c\instr,\TRUE))$).

\paragraph{Relation to \texttt{bf4}} The \texttt{bf4} algorithm is similar to
\textsc{VPreGen}, using formulae rather than examples. Rather than learn features, \texttt{bf4} uses a static set of
control-plane features (which they call ``atoms''). Then, rather than learn a
candidate boolean expression by abstracting these atoms and using a set of
concrete positive and negative examples, \texttt{bf4} uses Z3's unsat-core to
refine its candidate solution. Finally, \texttt{bf4} is interested in
bug-finding rather than verification so it computes necessary conditions rather
than sufficient conditions. The following table summarizes the differences

\begin{center}
\begin{tabular}{lll}
  \toprule
  & $\textsc{VPreGen}(c,Q,G)$ & \texttt{bf4's} $\textsc{INFER}(G,B,\mathcal P)$ \\
  \midrule \\
  Solution ($\varphi$)
  & $\{\varphi\} C \{Q\}$, and $\forall t \in G.\,\varphi(t)$
  & $G \models \phi$, minimizing(?) $|\{\eta\mid B
  \wedge \varphi\}|$ \\[1.5em]
  Features
  & dynamically learns features
  & features (aka \emph{atoms}) are heuristically defined ($\mathcal P$) \\[1.5em]
  Candidates &
  \begin{tabular}{>{\!\!\!}l}
    abstracts features; \\
    learns boolean expression; \\
    concretizes features
  \end{tabular}
  & iteratively negates Z3's unsat-core\\
  \bottomrule
\end{tabular}
\end{center}

\section{Can we use templates?}

One option is to use a kind of constrained template-based synthesis, where we
generate a catalogue of templates based on syntactic features of the target table.

@@

To do so, we need to extend our templates along the following dimensions:
\begin{enumerate}[align=left]
\item[\textit{Keys}.] Should generalize by changing the LHS comparisons to $
  \bigwedge_i[\rho.\keys[i]~\square_{\{=,\neq\}}~?_{v_i}]?$
\item[\textit{Action Data}.] Should generalize by changing the RHS comparisons to $\bigwedge_i[\rho.\data[i]~\square_{\{=,\neq\}}~?_{v_i}]?$
\item[\textbf{Actions}.] We need to generalize the template across multiple actions. This should be as simple as adding $\rho.\action = i$ on the RHS of each implication above.
\item[\textit{Sequence}.] I'm not sure how to generalize sequentially composed tables.
  Perhaps a larger catalogue of templates conditioned on structural information:
  if we notice that $t_1$ has a dataflow path to the keys of $t_2$, we should
  generate a join condition template, otherwise we may be able to simply ``and'' the templates.

\item[\textit{Nondeterminism} ($c_1 \choice c_2$).] To solve the \textbf{Conservative
  Problem} we simply and the templates together, but to solve the
  \textbf{Flexible Problem} we may be able to constrain the problem (by
  constraining the packets) to either $c_1$ or $c_2$. This would require
  computing a $b_{\textit{pkt}}$.
\end{enumerate}

\end{document}
m
